The complex structure and peculiar internal motions of the planetary nebula NGC 6210

### 2020-03-08 ms.tex
Minor changes to figures

The emission from the outer lobes is much fainter than the inner shells,
and is most easily detected in \oiii{}.
Figure~\ref{fig:outer-lobe-components} shows all the outer lobe velocity components
that we have been able to measure from the \oiii{} slits:
blue-shifted components in panel~a and red-shifted components in panel~b.
We have not included all of the \oiii{} components that lie outside the inner and intermediate shells, since some of these are closely associated with the low ionization knot complexes discussed above in \S~\ref{sec:knot-complexes}.
In these cases, the \oiii{} component is weaker than the corresponding \nii{} component,
slightly more spatially extended,
and with a velocity magnitude that is about \SI{5}{km.s^{-1}} smaller
(for both red and blue-shifted knots).
All such \oiii{} components are omitted from the figure 
with the exception of the N knot (see Fig.~\ref{fig:knot-complexes}),
which is positioned clearly within the N lobe.

As with the low-ionization knot complexes,
there are many apparent pairings between blue and red outer lobe components on opposite sides of the nebula.
This is illustrated in the lower panels of Figure~\ref{fig:outer-lobe-components},
where we classify the components into four high-velocity systems,
\Sys{1} to \Sys{4}
with \(|V| = \text{\SIrange{18}{25}{km.s^{-1}}}\) (panel~c)
and six intermediate-velocity systems,
\Sys{5} to \Sys{10}
with \(|V| = \text{\SIrange{5}{14}{km.s^{-1}}}\) (panel~d).
Nearly all of these systems have a blue and a red component
which are approximately symmetrically arranged about the central star.
For instance, the blue-shifted \SysM{2} component in the north
is paired with the red-shifted \SysP{2} component in the south.
Note, however, that \SysM{3} and \SysP{7} have no opposite counterparts.

>>>>

The emission from the outer lobes is much fainter than the inner shells,
and is most easily detected in \oiii{}.
Figure~\ref{fig:outer-lobe-components} shows all the outer lobe velocity components
that we have been able to measure from the \oiii{} slits:
blue-shifted components in panel~a and red-shifted components in panel~b.
We have not included all of the \oiii{} components that lie outside the inner and shells, since some of these are closely associated with the low ionization knot complexes discussed above in \S~\ref{sec:knot-complexes}.
In these cases, the \oiii{} component is weaker than the corresponding \nii{} component,
slightly more spatially extended,
and with a velocity magnitude that is about \SI{5}{km.s^{-1}} smaller
(for both red and blue-shifted knots).
Such \oiii{} components are omitted from the figure 
with the exception of the N knot and the NW knot (see Fig.~\ref{fig:knot-complexes}).

As with the low-ionization knot complexes,
there are many apparent pairings between blue and red outer lobe components on opposite sides of the nebula.
This is illustrated in the lower panels of Figure~\ref{fig:outer-lobe-components},
where we classify the components into four high-velocity systems,
\Sys{1} to \Sys{4}
with \(|V| = \text{\SIrange{17}{25}{km.s^{-1}}}\) (panel~c)
and six intermediate-velocity systems,
\Sys{5} to \Sys{10}
with \(|V| = \text{\SIrange{5}{14}{km.s^{-1}}}\) (panel~d).
Nearly all of these systems have a blue and a red component
which are approximately symmetrically arranged about the central star.
For instance, the blue-shifted \SysM{2} component in the north
is paired with the red-shifted \SysP{2} component in the south.
Note, however, that \SysM{3} and \SysP{7} have no opposite counterparts.
